Report and Figures

### 2016-11-12 figs.Rmd
updated tables for multigroup

tab %>% 
  mutate(percent_black = percent_black * 100) %>%   
  write_csv('figs/comparative_summary.csv')

@@

cluster_map_percent_black <- function(tracts_name, city, nclusters = 10){
	tracts <- readOGR(dsn = paste0('data/cities/',tracts_name), layer = 'geo', verbose = FALSE)

@@

tab %>% 
  write_csv('figs/clustering_summary.csv')

>>>>

# tab %>% 
#   mutate(percent_black = percent_black * 100) %>%   
#   write_csv('figs/comparative_summary.csv')
```
```{r}
cache %>% filter(city %in% c('Philadelphia', 'Atlanta')) %>% 
  select(city, H_Y, I_XY, J_XY) %>%
  mutate_at(.cols = c('H_Y', 'I_XY','J_XY'), 
            function(x) round(x, 2)) %>%
  write_csv('figs/comparative_summary.csv')
```

@@

```{r}
cluster_map_percent_black <- function(tracts_name, city, nclusters = 10){
	tracts <- readOGR(dsn = paste0('data/cities/',tracts_name), layer = 'geo', verbose = FALSE)

@@

tab %>% 
  write_csv('figs/clustering_summary.csv')s
```

```{r}
loss_curves %>% 
  group_by(city) %>% 
  filter(city %in% c('Atlanta', 'Philadelphia'),
         nclust %in% c(2, 5, 10)) %>% 
  select(-I_diff) %>% 
  mutate(I_XY = round(I_XY,2)) %>% 
  spread(key = city, value = I_XY, fill = NA) %>%
  write_csv('figs/clustering_summary.csv')
  # slice(match(nclust, c('2', '5', '10', 'I(X,Y)')))

loss_curves %>% 
  group_by(city) %>% 
  filter(city %in% c('Atlanta', 'Philadelphia')) %>% 
  summarise(`I(X,Y)` = max(I_XY)) %>% 
  spread(key = city, value = `I(X,Y)`, fill = NA) %>% 
  write_csv('figs/max_information.csv')
